Estimating individual subjective values of emotion regulation strategies

### 2023-07-06 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Estimating individual subjective values of emotion regulation strategies},
  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1,2, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.

@@

Data collection took place between 16th of August 2022 and the 3rd of February 2023.
A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
Of these, \(N=124\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of \(N=120\) participants (100 female; age: \(M\text{ }\pm\text{ }SD =22.5\text{ }\pm\text{ }3.0\) years old), which is 1.4 times more than what the highest sample size calculation required.
Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).

@@

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, \emph{corrugator} and \emph{levator} activity.
Descriptive values of each predictor for each condition can be found in Table \ref{tab:TabDescr}.
We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).

@@

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.77 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).

@@

Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
45.40\% of the participants stated that they chose the strategy that was easiest for them to implement.
24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found online on OSF (\url{https://osf.io/vnj8x/}).

@@

Individual SVs could be determined for 120 participants for all three ER strategies.
SVs ranged between 0.005 and 1.00.
\(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
Absolute preferences for ER strategies were relatively equally distributed.
Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 43.

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor subject accounted for 19.10\% of total variance.
The preregistered model showed a correlation of \(r=\) 0.95 between the random effects \emph{subjects} and \emph{recoded strategy} (\(BF10\) of the variable \emph{strategy}: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
Our model explained 90.4\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
\]

@@

\caption{\label{tab:TabMLMH5}Results of multilevel model predicting subjective values of ER strategies.}

@@

We then conducted an ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with \(R^{2}=\) 0.27.
The SV of the strategy distraction contributed significantly to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
The estimated odds ratio indicated a higher chance of choosing strategy distraction, when the SV of that strategy is higher.
Additionally, the predictor SV of the strategy suppression contributed significantly to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.

Last, we investigated whether SVs are associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
We found neither a significant association between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).

@@

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, which we have reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
\]
As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
Detailed information can be found in the supplementary material.

@@

Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
To establish the \emph{trait} nature of a measure, one could for instance resort to latent state trait modeling\textsuperscript{83}, as recently employed by our group in a related context\textsuperscript{30}.
The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation.
By definition, this represents a state.
As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also implies that SVs should differ according to situational factors (e.g.~stimulus intensity).
The ER goals that individuals pursue in a given situation must also be taken into account.
In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals\textsuperscript{85}.
Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also \protect\hyperlink{Limitations}{Limitations}).
Therefore, SVs may vary when different reference strategies are used.
It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals.
They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
Of course, it is also possible that such habits influence the internal formation of these subjective values.
However, our data are not suitable for answering this question.
In the future, SVs should therefore be collected in several similar situations.
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being\textsuperscript{9}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Estimating individual subjective values of emotion regulation strategies},
  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1,2, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the SV of the flexible strategy was set to 1, because that strategy was preferred when equal rewards were offered.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible strategy over the fixed strategy), the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
The resulting value of the flexible strategy was divided by 2€.
This yielded an SV of the fixed strategy between 0 and 1, with values closer to 0 indicating a stronger aversion to the fixed strategy compared to the flexible strategy.
The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.

@@

Data collection took place between the 16th of August 2022 and the 3rd of February 2023.
A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
The first session was attended by \(N=124\) participants\textsuperscript{34}, and \(N=121\) participants also completed the second session.
We excluded the data of \(n=1\) person from the present analyses because they stated that they did not follow the instructions.
Therefore, the final sample consisted of \(N=120\) participants (100 female; age: \(M\text{ }\pm\text{ }SD =22.5\text{ }\pm\text{ }3.0\) years old), which is 1.4 times more than what the highest sample size calculation required.
Please note that the sample size for a few analyses may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).

@@

To explore whether negative pictures evoked emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with the predictors subjective arousal, \emph{corrugator} and \emph{levator} activity.
Descriptive values of each predictor per condition can be found in Table \ref{tab:TabDescr}.
We found a significant main effect of valence on subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).

@@

To investigate whether ER strategies reduced emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
We found a significant main effect of strategy on subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.

@@

To investigate whether ER strategies required cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant main effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.77 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).

@@

Cognitive effort also played the most important role in the subsequent choice of strategy, which resembled previous findings of our group\textsuperscript{22}.
The majority of participants (45.40\%) stated that they chose the strategy that was easiest for them to implement, 24.40\% stated they chose the strategy that was most effective, and 11.80\% stated their chosen strategy was the easiest \emph{and} most effective.
A more detailed list of all reasons, including those given by participants who stated none of the three options above, can be found online on OSF (\url{https://osf.io/vnj8x/}).

@@

Individual SVs could be determined for 120 participants for all three ER strategies.
SVs ranged between 0.005 and 1.00.
Nearly all (\(n=\) 119) participants had one SV of 1.0, indicating a clear preference for one ER strategy over the other two.
Absolute preferences for ER strategies were relatively equally distributed: \(n=\) 41 participants assigned their highest SV to distraction, \(n=\) 36 to distancing, and \(n=\) 43 to suppression.

To investigate which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor \emph{subject} accounted for 19.10\% of total variance.
The preregistered model showed a correlation of \(r=\) 0.95 between the random effects \emph{subjects} and \emph{recoded strategy} (\(BF10\) of the variable \emph{strategy}: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
Our model explained 90.4\% of variance and thus we assumed our model was overfitted because we included \emph{recoded strategy} as the random slope.
We therefore set a new model without \emph{recoded strategy} as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
\]

@@

\caption{\label{tab:TabMLMH5}Results of the multilevel model predicting subjective values of ER strategies.}

@@

We then conducted an ordinal regression with the dependent variable \emph{choice} and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with \(R^{2}=\) 0.27.
The SV of the strategy distraction contributed significantly to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
The estimated odds ratio indicated a higher chance of choosing the strategy distraction when the SV of that strategy was higher.
Additionally, the predictor SV of the strategy suppression contributed significantly to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
The estimated odds ratio indicated that a participant was more likely to later choose suppression, when the SV of the strategy suppression was higher.

Lastly, we investigated whether SVs were associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual slopes and intercepts of ordered SVs could predict their ER flexibility score.
We found neither a significant association between slopes and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between intercepts and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).

@@

Because associations between self-control, the investment trait Need for Cognition (NFC), and both effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM reported above (Table \ref{tab:TabMLMH5}).
Only predictors that had previously shown a significant association with SVs were included in the model together with the level-2 predictors self-control and NFC.
The third model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
\]
The predictor effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)) and \emph{corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a positive association with SVs.
In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
However, the effect size of this effect was negligibly small (\(f^{2}=\) 0.002).
Detailed information can be found in Table S.10 in the supplementary material.

@@

Knowing whether the SVs of ER strategies have a trait character would allow a further evaluation of their practical relevance and predictive power.
With the data of the present study, a trait analysis is not possible, because the SVs of the ER strategies were assessed in only one situation at only one time point, which by definition represents a state.
A habit would imply consistency of SVs across time points in similar situations, whereas a trait would imply consistency across both time points and situations.
As noted above, ER choice behaviour is rather state-like, because it is influenced by personal regulatory goals, situational factors, and contextual demands\textsuperscript{21}.
We therefore believe that the influence of these factors on ER behaviour will also translate into state- or habit-like properties of SVs.
Such factors could be varied systematically in order to shed light on the stability of SVs, e.g.~by manipulating situational factors such as stimulus intensity, or by systematically assessing the goals that participants pursue with their ER behaviour.
As Wilms and colleagues\textsuperscript{72} pointed out, situational factors and ER goals are state-like themselves, because they vary greatly across time points and situations.
While participants in the lab mainly pursue hedonic but not social goals\textsuperscript{85}, a real-life situation with social goals is likely to change not only their ER behaviour but also the SVs they assign to different strategies, especially when their choice options are not restricted by the experimental design (see also \protect\hyperlink{Limitations}{Limitations}).
To investigate whether the SVs of ER strategies can be conceptualised as states, habits, or traits, one could employ latent state trait modelling, as recently done by our group in a related context\textsuperscript{30}.
A systematic (non-)variation of situational factors and the assessment of personal factors, e.g.~ER goals, can then help to disentangle time- and situation-specific variance in SVs.
Importantly, the practical relevance and predictive power of SVs should be assessed at every measurement, as it is quite possible that the correlation between SVs and ER choice is situation-specific as well.
Such findings would not only provide important insights into ER behaviour, but allow investigations into the association of ER behaviour with external criteria as well, such as well-being\textsuperscript{9}.
